Toward a clearer understanding of the inverse association between cancer and dementia

### 2021-04-29 06_presentations/ser2021/index.Rmd
retoques finales

- Participants between 60 and 70 years old at study entry, free of cancer and dementia diagnosis at baseline

@@

- Defining the underlying mechanism behind cancer diagnosis helps in multiple way.

  + Helps identify sources of bias and guides analysis

  + Opens conversations about future data collection

@@

  + The direct effect relies on the independent censoring assumption

@@

- Arfan M. Ikram

>>>>

- Participants between 60 and 70 years old at study entry, free of cancer and dementia diagnosis at baseline.

@@

- Defining the underlying mechanism behind cancer diagnosis helps in multiple ways.

  + Helps identify sources of bias and guides analysis.

  + Opens conversations about future data collection.

@@

  + The direct effect relies on the independent censoring assumption.

@@

- M. Arfan Ikram
